\begin{abstract}
Function approximation, optimization, and integration over (in)finite
domains are among the most fundamental mathematical problems. They  are
particularly challenging when the functions in consideration fluctuate
wildly in certain parts of the domain or if the domain is high dimensional.
Development of efficient and effective numerical algorithms for
approximating the solutions to these problems that are based on rigorous
mathematical frameworks, (statistical) error bounds, advanced sampling
strategies, and careful complexity analysis remain active research areas. 
The Guaranteed Automatic Integration Library (GAIL) %~\cite{ChoEtal18b} 
is our multi-year research efforts directed towards addressing the
aforementioned overarching theme. Briefly, GAIL is an open-source MATLAB
software package with eight main algorithms based on over ten peer-reviewed
publications, involving more than nine doctoral students and three faculty
members in Illinois Tech as well as their international collaborators.  The
theories behind our algorithms consider functions in cones, rather than
balls, and then proceed to sample data points of a given function in an
adaptive manner, placing more samples in areas where the function changes
faster. Our algorithms are iterative in nature, with errors bounds computed
in each iteration. They are proven to have optimal costs, with monotonic
decreasing error estimates and stop in the first iteration where user-given
tolerance is met.  We consistently employ proven industrial software
development practices for GAIL such as unit and integration tests,
searchable online and offline documentation, version control systems
(GitHub), and agile methodology (using Trello). Our reproducible research
have demonstrated that GAIL could outperform more established algorithms in
various ways.   
\end{abstract}